---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  geno: "no data"
  rep: "no data"
  block: "no data"
  k: "no data"
  data: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r, echo = FALSE}
library(knitr)

traits <- params$traits
geno <- params$geno
rep <- params$rep
block <- params$block
k <- params$k
data <- params$data
```

# 1. Model specification and data description

There are data for `r nlevels(as.factor(data[, geno]))` genotypes tested using an alpha (0,1) design with `r nlevels(as.factor(data[, rep]))` replications and `r nlevels(as.factor(data[, block]))` incomplete blocks. In this design each replication is a complete block for the genotypes that is splitted in several incomplete blocks. The statistical model is
$$
y_{ijk} = \mu + \tau_i + \gamma_j + \rho_{k(j)} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with genotype $i$, replication $j$, incomplete block $k$.
* $\mu$ is the mean response over all genotypes and replications.
* $\tau_i$ is the effect for genotype $i$.
* $\gamma_j$ is the effect for replication $j$.
* $\rho_{k(j)}$ is the effect of the incomplete block $k$ which is nested into replication $j$.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

```{r, include = FALSE}
out <- NULL
for (i in 1:length(traits))
  out <- c(out, knit_expand('child_a01d.Rmd'))
```

`r paste(knit(text = out), collapse = '\n')`
