`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r, echo = FALSE}
lc <- check.abd(traits[i], geno, rep, data)

if (lc$nt.check.0 > 0) {
    cond <- !(data[, geno] %in% lc$check.0) & !is.na(data[, traits[i]])
    temp <- subset(data, cond)
  } else {
    cond <- !is.na(data[, traits[i]])
    temp <- subset(data, cond)
  }

if (lc$nt.check.1 > 0){
  cond <- !(temp[, geno] %in% lc$check.1)
  temp <- subset(temp, cond)
}

y <- temp[, traits[i]]
model <- agricolae::DAU.test(factor(temp[, rep]), factor(temp[, geno]), y)
```

## {{i+1}}.1. General setting

`r if(lc$nmis.new == 0 & lc$nmis.check == 0) {"For this trait there is no missing values."}`
`r if(lc$nmis.new == 1) {"There is one genotype with missing value. This genotype has been removed."}`
`r if(lc$nmis.new > 1) paste("There are", lc$nmis.new, "genotypes with missing values. These genotypes have been removed.")`
`r if(lc$nmis.new > 0) paste("Therefore, there are", lc$nt.new - lc$nmis.new, "genotypes included in the analysis.")`

`r if(lc$nt.check.0 == 1) paste("There is one check without data: ", lc$check.0, ". This check has been removed.", sep = "")`
`r if(lc$nt.check.0 > 1) paste("There are ", lc$nt.check.0, " checks without data: ", sep = "")`
```{r, echo = FALSE}
if(lc$nt.check.0 > 1) lc$check.0
```
`r if(lc$nt.check.0 > 1) {"These checks have been removed."}`

`r if(lc$nt.check.1 == 1) paste("There is one check with data in only one block: ", lc$check.1, ". Checks need at least two replications so this check has been removed.", sep = "")`
`r if(lc$nt.check.1 > 1) paste("There are ", lc$nt.check.1, " checks with data in only one block: ", sep = "")`
```{r, echo = FALSE}
if(lc$nt.check.1 > 1) lc$check.1
```
`r if(lc$nt.check.1 > 1) {"Checks need at least two replications so these checks have been removed."}`

## {{i+1}}.2. Adjusted means

```{r, echo = FALSE}
model$means
```

## {{i+1}}.3. Overall mean and CV

```{r, echo = FALSE}
model$statistics
```

## {{i+1}}.4. LSD test

```{r, echo = FALSE}
model$groups
```
