---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  traits: "no data"
  A: "no data"
  B: "no data"
  rep: "no data"
  design: "no data"
  data: "no data"
  maxp: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r, echo = FALSE}
library(knitr)

traits <- params$traits
A <- params$A
B <- params$B
rep <- params$rep
design <- params$design
data <- params$data
maxp <- params$maxp

data[, A] <- as.character(data[, A])
data[, B] <- as.character(data[, B])
data[, rep] <- as.character(data[, rep])
```

# 1. Model specification and data description

The data frame has two factors with `r nlevels(as.factor(data[, A]))` and `r nlevels(as.factor(data[, B]))` levels. The experimental design is a completely randomized design with `r nlevels(as.factor(data[, rep]))` replications. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with level $i$ of factor A, level $j$ of factor B, and replication $k$.
* $\mu$ is the mean response over all levels of factor A, factor B, and replications.
* $\alpha_i$ is the effect for level $i$ of factor A.
* $\beta_j$ is the effect for level $j$ of factor B.
* $(\alpha\beta)_{ij}$ is the interaction effect between level $i$ of factor A and level $j$ of factor B.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

```{r, include = FALSE}
out <- NULL
for (i in 1:length(traits)) {
  lc <- check.2f(traits[i], A, B, rep, data)
  if (lc$c1 == 1 & lc$c2 == 1 & lc$c3 == 1 & lc$pmis <= maxp)
    out <- c(out, knit_expand('child_2f.Rmd'))
  else
    out <- c(out, knit_expand('child_2f_fail.Rmd'))
}
```

`r paste(knit(text = out), collapse = '\n')`
