---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  traits: "no data"
  factors: "no data"
  rep: "no data"
  dfr: "no data"
  maxp: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
factors <- params$factors
rep <- params$rep
dfr <- params$dfr
maxp <- params$maxp

# Check factors structure

out <- ck.fs(factors, rep, dfr)
dfr <- out$dfr
nla <- out$nl[1]
nlb <- out$nl[2]
nrep <- out$nrep
nmis.fac <- out$nmis.fac

# Everything as character

dfr[, factors[1]] <- as.character(dfr[, factors[1]])
dfr[, factors[2]] <- as.character(dfr[, factors[2]])
```

# 1. Model specification and data description

The data frame has two factors with `r nla` and `r nlb` levels. The experimental design is a completely randomized design with `r nrep` replications. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with level $i$ of factor A, level $j$ of factor B, and replication $k$.
* $\mu$ is the mean response over all levels of factor A, factor B, and replications.
* $\alpha_i$ is the effect for level $i$ of factor A.
* $\beta_j$ is the effect for level $j$ of factor B.
* $(\alpha\beta)_{ij}$ is the interaction effect between level $i$ of factor A and level $j$ of factor B.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "rows with missing values for classifications factors. These rows have been deleted.")`

```{r include = FALSE}
out <- NULL
for (i in 1:length(traits)) {
  lc <- ck.f(traits[i], factors, rep, dfr)
  if (lc$nt.0 == 0 & lc$nrep > 1 & lc$nt.mult == 0 & lc$pmis <= maxp) {
    out <- c(out, knit_expand('child_f.Rmd'))
  } else {
    out <- c(out, knit_expand('child_f_fail.Rmd'))
  }
}
```

`r paste(knit(text = out), collapse = '\n')`
