---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  geno: "no data"
  rep: "no data"
  dfr: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
geno <- params$geno
rep <- params$rep
dfr <- params$dfr

# Remove rows with missing values for factors

out <- ck.fs(geno, rep, dfr)
dfr <- out$dfr
nmis.fac <- out$nmis.fac

# Identify checks and no checks

temp <- data.frame(table(dfr[, geno]))
lg.ck <- temp[temp$Freq > 1, 1]
lg <- temp[temp$Freq == 1, 1]

# Number of checks, no checks, and replications

ng.ck <- length(lg.ck)
ng <- length(lg)
nrep <- length(unique(dfr[, rep]))
```

# 1. Model specification and data description

There are data for `ng` genotypes tested using an augmented block design with `nrep` blocks and `ng.ck` checks in each block. The statistical model is
$$
y_{ij} = \mu + \tau_i + \beta_j + \epsilon_{ij}
$$
where

* $y_{ij}$ is the observed response with genotype $i$ and block $j$.
* $\mu$ is the mean response over all genotypes and blocks.
* $\tau_i$ is the effect for genotype $i$.
* $\beta_j$ is the effect for block $j$.
* $\epsilon_{ij}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ij} \sim N(0,\sigma_{\epsilon}^2)$.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "rows with missing values for classifications factors. These rows have been deleted.")`

```{r include = FALSE}
out <- NULL

for (i in 1:length(traits)) {
  
  lc <- ck.abd(traits[i], geno, rep, dfr)

  if (lc$nck.2 > 1) {
    out <- c(out, knit_expand('child_abd.Rmd'))
  } else {
    out <- c(out, knit_expand('child_abd_fail.Rmd'))
  }
}
```

`r paste(knit(text = out), collapse = '\n')`
