`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r echo = FALSE}
lc <- ck.f(traits[i], c(geno, env), rep, dfr)
```

`r if (lc$nrep == 1) {"There is only one replication. Analysis is not possible with one replication."}`

`r if (lc$nrep > 1 & lc$nt.mult > 0) {"There is more than one datum for at least one combination of the genotypes and environments in at least one replication. This could be the result of a mislabeling for the levels of the factors. The table below shows the frequencies of valid data for each genotype and environment in each replication."}`

`r if (lc$nt.0 > 0 & lc$nrep > 1 & lc$nt.mult == 0) {"There is at least one genotype without data in at least one environment. The table below shows the frequencies of valid data for each genotype in each environment. A MET analysis cannot be produced if there are combination of genotypes and environments without data."}`

`r if (lc$pmis > maxp & lc$nt.0 == 0 & lc$nrep > 1 & lc$nt.mult == 0) paste0("There are too many missing values (", format(lc$pmis * 100, digits = 3), "%). The table below shows the frequencies of valid data for each genotype in each environment. This procedure estimates up to 10%.")`

```{r echo = FALSE}
if (lc$nrep > 1 & lc$nt.mult == 0)
  lc$tf
if (lc$nrep > 1 & lc$nt.mult > 0)
  lc$tfr
```
