`r i = {{i}}`

# {{i+1}}. Analysis for trait `r traits[i]`

```{r echo = FALSE}
lc <- ck.f(traits[i], factors, rep, dfr)
```

`r if (lc$nrep == 1) {"There is only one replication. Analysis is not possible with one replication."}`

`r if (lc$nrep > 1 & lc$nt.mult > 0) {"There is more than one datum for at least one combination of the factors in at least one replication. This could be the result of a mislabeling for the levels of the factors. The table below shows the frequencies of valid data for each combination of the levels of the factors in each replication."}`

`r if (lc$nt.0 > 0 & lc$nrep > 1 & lc$nt.mult == 0) {"There is at least one combination of the factors without data. The table below shows the frequencies of valid data for each combination of the levels of the factors. The analysis cannot be produced if there are combinations of the factors without data."}`

`r if (lc$pmis > maxp & lc$nt.0 == 0 & lc$nrep > 1 & lc$nt.mult == 0) paste0("There are too many missing values (", format(lc$pmis * 100, digits = 3), "%). The table below shows the frequencies of valid data for each combination of the levels of the factors. This procedure estimates up to 10%.")`

```{r echo = FALSE}
if (lc$nrep > 1 & lc$nt.mult > 0)
  lc$tfr
if (lc$nrep > 1 & lc$nt.mult == 0)
  lc$tf
```
