---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  trt: "no data"
  trt.lab: "no data"
  dfr: "no data"
  maxp: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
trt <- params$trt
trt.lab <- params$trt.lab
nct <- nchar(trt.lab)
trt.lab.s <- paste0(trt.lab, "s")
trt.lab.c <- paste0(toupper(substr(trt.lab, 1, 1)), substr(trt.lab, 2, nct))
trt.lab.sc <- paste0(toupper(substr(trt.lab, 1, 1)), substr(trt.lab, 2, nct), "s")
dfr <- params$dfr
maxp <- params$maxp

# Check factors structure

out <- ck.fs(trt, NULL, dfr)
nt <- out$nl[[1]]
dfr <- out$dfr
nmis.fac <- out$nmis.fac
```

# 1. Model specification and data description

There are data from `r nt` `r trt.lab.s` evaluated using a completely randomized design. The statistical model is
$$
y_{ij} = \mu + \tau_i + \epsilon_{ij}
$$
where

* $y_{ij}$ is the observed response with `r trt.lab` $i$ and replication $j$.
* $\mu$ is the mean response over all `r trt.lab.s` and replications.
* $\tau_i$ is the effect for `r trt.lab` $i$.
* $\epsilon_{ij}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ij} \sim N(0,\sigma_{\epsilon}^2)$.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "rows with missing values for classifications factors. These rows have been deleted.")`


```{r include = FALSE}
out <- NULL
for (i in 1:length(traits)) {
  lc <- ck.crd(traits[i], trt, dfr)
  if (lc$ng.0 == 0 & lc$nrep > 1 & lc$ng > 2) {
    out <- c(out, knit_expand('child_crd.Rmd'))
  } else {
    out <- c(out, knit_expand('child_crd_fail.Rmd'))
  }
}
```

`r paste(knit(text = out), collapse = '\n')`
