---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    toc: true
    toc_depth: 3
    highlight: "tango"
params:
  traits: "no data"
  geno: "no data"
  env: "no data"
  rep: "no data"
  dfr: "no data"
  maxp: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
geno <- params$geno
env <- params$env
rep <- params$rep
dfr <- params$dfr
maxp <- params$maxp

# Check factors structure

out <- ck.fs(c(geno, env), rep, dfr)
dfr <- out$dfr
nl <- out$nl
nrep <- out$nrep
nmis.fac <- out$nmis.fac

# Everything as character

dfr[, geno] <- as.character(dfr[, geno])
dfr[, env] <- as.character(dfr[, env])
dfr[, rep] <- as.character(dfr[, rep])
```

# 1. Model specification and data description

The data frame has `r nl[2]` environments and `r nl[1]` genotypes. In each environment the genotypes were evaluated using a randomized complete block design with `r nrep` blocks. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + (\alpha\beta)_{ij} + \gamma_{k(j)} + \epsilon_{ijk}
$$
where

* $y_{ijk}$ is the observed response with genotype $i$, environment $j$, and block $k$ nested in environment $j$.
* $\mu$ is the mean response over all genotypes, environments and blocks.
* $\alpha_i$ is the effect for genotype $i$.
* $\beta_j$ is the effect for environment $j$.
* $(\alpha\beta)_{ij}$ is the interaction effect between genotype $i$ and environment $j$.
* $\gamma_{k(j)}$ is the effect of block $k$ nested in environment $j$.
* $\epsilon_{ijk}$ is the error term.

In this model we assume that the errors are independent and have a normal distribution with common variance, that is, $\epsilon_{ijk} \sim N(0,\sigma_{\epsilon}^2)$.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "rows with missing values for classifications factors. These rows have been deleted.")`

```{r include = FALSE}
out <- NULL
for (i in 1:length(traits)) {
  lc <- ck.f(traits[i], c(geno, env), rep, dfr)
  if (lc$nt.0 == 0 & lc$nrep > 1 & lc$nt.mult == 0 & lc$pmis <= maxp) {
    out <- c(out, knit_expand('child_met.Rmd'))
  } else {
    out <- c(out, knit_expand('child_met_fail.Rmd'))
  }
}
```

`r paste(knit(text = out), collapse = '\n')`
