---
title: "Report for a numeric trait"
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
  pdf_document:
    toc: true
    highlight: zenburn
  word_document:
    highlight: "tango"
params: 
  x: "no data"
  author: "no data"
---

```{r echo = FALSE}
# Some parameters
p1 <- length(params$x)
p2 <- max(table(params$x))
p3 <- length(table(params$x))
```

It looks like you have a numeric trait. You can see a descriptive summary below:
```{r echo = FALSE}
output <- summary(params$x)
output
```

```{r echo = FALSE}
sk <- 3 * (mean(params$x) - median(params$x)) / sd(params$x)
```

`r if (sk > 0.5) {"It looks like you have some positive skewness because your mean is quite larger than your median. Watch out with this if you want to fit a model that assumes normality." }`

`r if (sk < -0.5) {"It looks like you have some negative skewness because your mean is quite smaller than your median. Watch out with this if you want to fit a model that assumes normality." }`

`r if (p1 > 25 & (p1 / p3 <= 2 | (p1 / p3 > 2 & p3 > 20))) {"A boxplot could be a suitable plot for these data:"}`

```{r echo = FALSE}
if (p1 > 25 & (p1 / p3 <= 2 | (p1 / p3 > 2 & p3 > 20)))
  boxplot(params$x)
```
`r if (p1 > 25 & p1 / p3 > 2 & p3 <= 20) {"For this trait a frequency table could produce a good display of the data:"}`

```{r echo = FALSE}
if (p1 > 25 & p1 / p3 > 2 & p3 <= 20)
  table(params$x)
```

`r if(p1 <= 25) {"A dotplot could be a suitable plot for these data:"}`

```{r echo = FALSE}
if (p1 <= 25)
  stripchart(params$x)
```

`r if (p1 > 25 & p1 / p3 < 2 & p2 / p1 > 0.05) {"Although your trait seems to be on a continuous scale, there are some values with a very high frequency. What out with this if you plan to fit a model that assumes normality. You can see these values and their frequency below:"}`

```{r echo = FALSE}
if (p1 > 25 & p1 / p3 < 2 & p2 / p1 > 0.05)
  table(params$x)[table(params$x) / p1 > 0.05]
```
