---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  mpf: "no data"
  spf: "no data"
  sspf: "no data"
  rep: "no data"
  dfr: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
mpf <- params$mpf
spf <- params$spf
sspf <- params$sspf
rep <- params$rep
dfr <- params$dfr

# Check factors structure

out <- ck.fs(c(mpf, spf, sspf), rep, dfr)
nmpf <- out$nl[[1]]
nspf <- out$nl[[2]]
nsspf <- out$nl[[3]]
nrep <- out$nrep
dfr <- out$dfr
nmis.fac <- out$nmis.fac

# Define internal variables

mpf <- dfr[, mpf]
spf <- dfr[, spf]
sspf <- dfr[, sspf]
rep <- dfr[, rep]
```

# 1. Model specification and data description

There are data for a split-split-plot design with `r nmpf` levels for the main plot factor, `r nspf` levels for the sub-plot factor, `r nsspf` levels for the sub-sub-plot factor, and `r nrep` replications for the main plot factor. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + \gamma_k + \delta_l + (\alpha\beta)_{ij} + (\alpha\gamma)_{ik} + (\alpha\delta)_{il} + (\beta\gamma)_{jk} + (\beta\delta)_{jl} + (\gamma\delta)_{kl} \\
+ (\alpha\beta\gamma)_{ijk} + (\alpha\beta\delta)_{ijl} + (\alpha\gamma\delta)_{ikl} + (\beta\gamma\delta)_{jkl} + (\alpha\beta\gamma\delta)_{ijkl}
$$
where

* $y_{ijkl}$ is the observed response with level $i$ of the main plot factor, level $j$ of the sub-plot factor, level $k$ of the sub-sub-plot factor, and replication $l$.
* $\mu$ is the mean response over all levels of factors and replications.
* $\alpha_i$ is the effect for level $i$ of the main plot factor.
* $\beta_j$ is the effect for level $j$ of the sub-plot factor.
* $\gamma_k$ is the effect for level $k$ of the sub-sub-plot factor.
* $\delta_l$ is the effect of replication $l$.
* $(\alpha\beta)_{ij}$, $(\alpha\gamma)_{ik}$, $(\alpha\delta)_{il}$, $(\beta\gamma)_{jk}$, $(\beta\delta)_{jl}$, $(\gamma\delta)_{kl}$, $(\alpha\beta\gamma)_{ijk}$, $(\alpha\beta\delta)_{ijl}$, $(\alpha\gamma\delta)_{ikl}$, $(\beta\gamma\delta)_{jkl}$, and $(\alpha\beta\gamma\delta)_{ijkl}$ the corresponding interactions.

In this model $(\alpha\delta)_{il}$ is the error term for the main plot factor, $(\beta\delta)_{jl}$ and $(\alpha\beta\delta)_{ijl}$ are pooled to form the error term for the split-plot factor, and $(\gamma\delta)_{kl}$, $(\alpha\gamma\delta)_{ikl}$, $(\beta\gamma\delta)_{jkl}$, and $(\alpha\beta\gamma\delta)_{ijkl}$ are pooled to form the error term for the sub-sub-plot factor.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "data row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "data rows with missing values for classifications factors. These rows have been deleted.")`

```{r include = FALSE}
out <- NULL
for (i in 1:length(traits))
  out <- c(out, knit_expand('child_spld.Rmd'))
```

`r paste(knit(text = out), collapse = '\n')`
