---
title: "`r params$title`"
subtitle: '`r params$subtitle`'
author: '`r params$author`'
date: '`r format(Sys.time(), "%B %d, %Y")`'
output: 
  html_document:
    theme: united
    toc: true
    toc_depth: 3
  pdf_document:
    toc: true
    toc_depth: 3
    highlight: zenburn
  word_document:
    highlight: "tango"
    toc: true
    toc_depth: 3
params: 
  traits: "no data"
  rowf: "no data"
  colf: "no data"
  rep: "no data"
  dfr: "no data"
  title: "no data"
  subtitle: "no data"
  author: "no data"
---

```{r echo = FALSE}
library(knitr)

# Pass arguments

traits <- params$traits
rowf <- params$rowf
colf <- params$colf
rep <- params$rep
dfr <- params$dfr

# Check factors structure

out <- ck.fs(c(rowf, colf), rep, dfr)
nrf <- out$nl[[1]]
ncf <- out$nl[[2]]
nrep <- out$nrep
dfr <- out$dfr
nmis.fac <- out$nmis.fac

# Define internal variables

rowf <- dfr[, rowf]
colf <- dfr[, colf]
rep <- dfr[, rep]
```

# 1. Model specification and data description

There are data for a strip plot design with `r nrf` level for the row factor, `r ncf` levels for the column factor, and `r nrep` replications. In this design each replication is a complete block for the levels of each factor. The statistical model is
$$
y_{ijk} = \mu + \alpha_i + \beta_j + \gamma_k + (\alpha\beta)_{ij} + (\alpha\gamma)_{ik} + (\beta\gamma)_{jk} + (\alpha\beta\gamma)_{ijk}
$$
where

* $y_{ijk}$ is the observed response with level $i$ of the row factor, level $j$ of the column factor, and replication $k$.
* $\mu$ is the mean response over all levels of factors and replications.
* $\alpha_i$ is the effect for level $i$ of the row factor.
* $\beta_j$ is the effect for level $j$ of the column factor.
* $\gamma_k$ is the effect of replication $k$.
* $(\alpha\beta)_{ij}$, $(\alpha\gamma)_{ik}$, $(\beta\gamma)_{jk}$, and $(\alpha\beta\gamma)_{ijk}$ the corresponding interactions.

In this model $(\alpha\gamma)_{ik}$, $(\beta\gamma)_{jk}$, and $(\alpha\beta\gamma)_{ijk}$ are the errors used to test the row factor, the column factor, and the row and column factors interaction respectively.

`r if (nmis.fac == 1) paste("Note: There is", nmis.fac, "data row with missing values for classifications factors. This row has been deleted.")`
`r if (nmis.fac > 1) paste("Note: There are", nmis.fac, "data rows with missing values for classifications factors. These rows have been deleted.")`

```{r include = FALSE}
out <- NULL
for (i in 1:length(traits))
  out <- c(out, knit_expand('child_strd.Rmd'))
```

`r paste(knit(text = out), collapse = '\n')`
